Considering scale in multilayer animal social networks

### 2020-06-25 paper/manuscript.Rmd
fix lc fig cap
abstract edits

Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can range from fine-scale
interactions to co-occurrence and overlapping home ranges. <!-- and vary within and 
across seasons.--> Multilayer networks promise the explicit integration
of the social, spatial and temporal contexts multilayer social networks. 
Given the complex interplay of
sociality and animal space use in heterogeneous landscapes, there remains 
an important gap in our understanding of the influence of scale on animal
social networks. Here we discuss social, spatial and temporal scale in the 
context of multilayer caribou social networks. <!--We also present perspectives on
future development and applications of scale in multilayer networks with respect
to: phenotypes and individual fitness, movement ecology and collective movement,
and habitat selection and space use.--> Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research. Here, we
incorporate perspectives on how the social environment and spatial processes
are linked across scales in a multilayer context.

>>>>

Scale remains a foundational concept in ecology. Spatial scale, for instance,
has become a central consideration in the way we understand landscape ecology
and animal space use. Meanwhile, social processes can range from fine-scale
interactions to co-occurrence and overlapping home ranges. <!-- and vary within and 
across seasons.--> Multilayer networks promise the explicit integration
of the social, spatial and temporal contexts. 
Given the complex interplay of
sociality and animal space use in heterogeneous landscapes, there remains 
an important gap in our understanding of the influence of scale on animal
social networks. We discuss ways of considering social, spatial and temporal scale in the 
context of multilayer caribou social networks. <!--We also present perspectives on
future development and applications of scale in multilayer networks with respect
to: phenotypes and individual fitness, movement ecology and collective movement,
and habitat selection and space use.--> Effective integration of social and spatial
processes, including biologically meaningful scales, within the context of
animal social networks is an emerging area of research. We
incorporate perspectives on how the social environment and spatial processes
are linked across scales in a multilayer context.
